### 2020-11-21 experiments.tex
updates

Figure \ref{fig:solidityvenn} shows the mutants killed by the Solidity analysis tools.  Table \ref{tab:scoresolidity} provides numeric details of the results, including the \emph{ratio} for each tool, adjusting its mutation scores by its' general tendency to produce findings.  The second row for each tool shows the number of contracts for which it reported no findings, and the mutation scores over those contracts, only. A user examining these results would suspect that Slither and SmartCheck are both useful tools, and should likely both be applied in a high-risk security-sensitive context like smart contract development.  A user might also suspect that the large number of findings produced, and smaller number of mutants killed, for Securify, means that whether to apply Securify is a more difficult decision.  On the one hand, Securify does detect nearly as many mutants it alone can identify as SmartCheck.  The large number of findings, and very bad mutant ratio, however, lead us to suspect that many of these ``detected'' mutants are false positives (or, at least, that the problem is not the one Securify identifies).  Extracting the signal from Securify's noise will be difficult.  We also note that while running Slither and SmartCheck on all 46,769 valid mutants was relatively quick (it took about 6 days sequential compute time for Slither and 3 days for SmartCheck, i.e., about 5-15 seconds per mutant for both tools), Securify often required many hours to analyze a mutant, and frequently required a few days to analyze a mutant; the full analysis required over three months of compute time.

@@

{\bf RQ2} is also answered in the affirmative.  Counting findings for un-mutated code might suggest that Securify is the best tool, by a wide margin, but in the context of its near-zero mutant ratio, we must suspect (and we partially manually confirmed) that many of the warnings are false positives.  Slither has the best mutant ratio, but the margin between it and SmartCheck confirms that both tools likely provide value.

@@

Figure \ref{fig:javavenn} shows the mutants killed by the Java analysis tools, and Table \ref{tab:scorejava} provides numeric results for projects and clean projects, respectively.

@@

Figure \ref{fig:pythonvenn} shows the mutants killed by the Python analysis tools, and Table \ref{tab:scorepython} provides numeric results for projects and clean projects, respectively.

>>>>

Figure \ref{fig:solidityvenn} shows the mutants killed by the Solidity analysis tools.  Table \ref{tab:scoresolidity} provides numeric details of the results, including the \emph{ratio} for each tool, adjusting its mutation scores by its' general tendency to produce findings.  The second row for each tool shows the number of contracts for which it reported no findings, and the mutation scores over those contracts, only. A user examining these results would suspect that Slither and SmartCheck are both useful tools, and should likely both be applied in a high-risk security-sensitive context like smart contract development.  A user might also suspect that the large number of findings produced, and smaller number of mutants killed, for Securify, means that whether to apply Securify is a more difficult decision.  On the one hand, Securify does detect nearly as many mutants it alone can identify as SmartCheck.  The large number of findings, and very bad mutant ratio, however, lead us to suspect that many of these ``detected'' mutants are false positives (or, at least, that the problem is not the one Securify identifies).  Extracting the signal from Securify's noise will be difficult.  We also note that while running Slither and SmartCheck on all 46,769 valid mutants was relatively quick (it took about 6 days sequential compute time for Slither and 3 days for SmartCheck, i.e., about 5-15 seconds per mutant for both tools), Securify often required many hours to analyze a mutant, and frequently required a few days to analyze a mutant; the full analysis required over three months of compute time.  However, similar statistical results would almost certainly be produced by running as few as 1,000 mutants, randomly selected, due to the implications of Tchebysheff’s inequality \cite{gopinath2015hard}, a technique that should improve scalability for all such analyses.

If we consider results at the individual contract level, the overall picture is in some ways even clearer.  Slither detected more mutants than Securify for 84 of the contracts, and more than SmartCheck for 85 of the contracts.  SmartCheck detected more mutants than Securify for 83 of the contracts.  Comparing ratios instead, Slither was better than Security for 97 contracts, but better than SmartCheck for only 75 of the contracts.  SmartCheck's ratio was better than Securify's for 95 contracts.  The standard deviation of contract raw scores was 0.05 for Slither, 0.03 for SmartCheck, and 0.04 for Securify.

@@

{\bf RQ2} is also answered in the affirmative.  Counting findings for un-mutated code might suggest that Securify is the best tool, by a wide margin, but in the context of its near-zero mutant ratio, we must suspect (and we partially manually confirmed) that many of the warnings are false positives.  Slither has the best mutant ratio, but the margin between it and SmartCheck confirms that both tools likely provide value; we note there is a 25\% chance that SmartCheck has a better ratio than Slither for an individual contract.

@@

Figure \ref{fig:javavenn} shows the mutants killed by the Java analysis tools, and Table \ref{tab:scorejava} provides numeric results for projects and clean projects, respectively.  At the individual project level, Infer was never best; PMD had a better raw score than SpotBugs for 10 of the 15 projects, but SpotBug had a better ratio for 11 of the projects.  There is perhaps a real tradeoff in verbosity and precision here.  Standard deviation in project mutation scores was 0.05 for SpotBugs, 0.04 for PMD, and 0 for Infer.

@@

Figure \ref{fig:pythonvenn} shows the mutants killed by the Python analysis tools, and Table \ref{tab:scorepython} provides numeric results for projects and clean projects, respectively.  At the project level, Pylint was better than pyflakes and PyChecker for 22 of 25 projects each by raw score, and better by ratio for 23 and 22 projects, respectively.  PyChecker was better than pyflakes for 15 projects, by both raw and ratio measures.  Standard deviations in mutation scores were high for Python:  0.15 for Pylint, 0.06 for pyflakes, and 0.27 for PyChecker.
